Approximation as Differentiation notes

### 2025-02-10 notes/definitions.tex
Two different functors..

For a functor $F: C \to \Set$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $C$ and an $I$-indexed family $X \in FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(X) = Y$.
\end{itemize}

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$ for the special case where $F: C
\to \Set$ (where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete
categories).

@@

\noindent This is the Grothendieck construction for the functor $\Set^{\op} \to \Cat$ which sends any set $I$
to the category $\Fam(I,C)$ and any function $f: I \to J$ to the reindexing functor $-[f]: \Fam(J,C) \to
\Fam(I,C)$.

>>>>

For a functor $F: C \to \Cat$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $C$ and an $I$-indexed family $X \in FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(X) = Y$.
\end{itemize}

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$.

@@

\noindent This is the Grothendieck construction for the functor $\Fam(-,C)$.
